### 2016-07-17 Docs/architecture/architecture.tex
helmeos -> helmholtz

  \item {\tt Microphysics/}

    The core microphysics routines used by \maestro.  These are organized
    into the following sub-directories.

@@

      A collection of various EOSes for use with the code.  The two
      important ones for \maestro\ are {\tt helmeos/} and {\tt
        gamma\_law\_general/}.

@@

      Various reaction networks for \maestro\ problems.  In addition
      to providing a routine to evolve the nuclear species due to
      reactions, the networks also define the species that are
      advected by the code.

@@

A \maestro\ application is built from several packages (the
multigrid solver, an EOS, a reaction network, etc.).  The core
\maestro\ packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem-specific files.  
\begin{lstlisting}[language={[gnu]make},mathescape=false]
EOS_DIR := helmeos   
CONDUCTIVITY_DIR := constant
NETWORK_DIR := ignition_simple

EXTRA_DIR := Util/random
\end{lstlisting}
Note that the microphysics packages are listed simply by the name of 
the directory containing the specific implementation (e.g. {\tt helmeos}).
By default, the build system will look in {\tt Microphysics/EOS/} for
the EOS, {\tt Microphysics/conductivity/} for the conductivity routine,
and {\tt Microphysics/networks/} for the reaction network.  To
override this default search path, you can set {\tt EOS\_TOP\_DIR},
{\tt CONDUCTIVITY\_TOP\_DIR}, and {\tt NETWORK\_TOP\_DIR} respectively.

@@

Some packages (for instance, the {\tt helmeos}
EOS) require Fortran include files.  The {\tt Fmincludes} variable
lists all those directories that contain include files that are
inserted into the Fortran source at compile time via the {\tt include}
statement.  Presently, the only instance of this is with the Helmholtz
general equation of state found in {\tt Microphysics/EOS/helmeos/}.  This is
automatically handled by the {\tt GMaestro.mak} instructions.

@@

Presently there is a single EOS that comes with \maestro, {tt gamma\_law\_general},
but many more are available through the external \microphysics\ repo\footnote{\microphysics\ is
available at \url{https://github.com/BoxLib-Codes/Microphysics}.  \maestro\ will
find it via the {\tt MICROPHYSICS\_HOME} environment variable}.  The \microphysics\
EOSs share the same interface and can be compiled into \maestro\ directly.  
Here are the more popular EOSs:
\begin{itemize}
\item {\tt helmeos} represents a general stellar equation 
      of state, consisting of nuclei (as an ideal gas), radiation,
      and electrons (with arbitrary degeneracy and degree of relativity).
      This equation of state is that described in \cite{timmes_eos}.

>>>>

  \item {\tt Microphysics/}\footnote{Note: many more \compatible\ routines are available in the separate \microphysics\ git repo}

    The basic microphysics routines used by \maestro.  These are organized
    into the following sub-directories.

@@

      The {\tt gamma\_law\_general/}.

@@

      The basic {\tt general\_null} network that defines arbitrary
      non-reacting species.

@@

A \maestro\ application is built from several packages (the
multigrid solver, an EOS, a reaction network, etc.).  The core
\maestro\ packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem-specific files.  
\begin{lstlisting}[language={[gnu]make},mathescape=false]
EOS_DIR := helmholtz   
CONDUCTIVITY_DIR := constant
NETWORK_DIR := ignition_simple

EXTRA_DIR := Util/random
\end{lstlisting}
Note that the microphysics packages are listed simply by the name of 
the directory containing the specific implementation (e.g. {\tt helmholtz}).
By default, the build system will look in {\tt Microphysics/EOS/} for
the EOS, {\tt Microphysics/conductivity/} for the conductivity routine,
and {\tt Microphysics/networks/} for the reaction network.  To
override this default search path, you can set {\tt EOS\_TOP\_DIR},
{\tt CONDUCTIVITY\_TOP\_DIR}, and {\tt NETWORK\_TOP\_DIR} respectively.

@@

Some packages (for instance, the {\tt helmholtz}
EOS) require Fortran include files.  The {\tt Fmincludes} variable
lists all those directories that contain include files that are
inserted into the Fortran source at compile time via the {\tt include}
statement.  Presently, the only instance of this is with the Helmholtz
general equation of state found in {\tt Microphysics/EOS/helmholtz/}.  This is
automatically handled by the {\tt GMaestro.mak} instructions.

@@

Presently there is a single EOS that comes with \maestro, {tt gamma\_law\_general},
but many more are available through the external \microphysics\ repo\footnote{\microphysics\ is
available at \url{https://github.com/BoxLib-Codes/Microphysics}.  \maestro\ will
find it via the {\tt MICROPHYSICS\_HOME} environment variable}.  The \microphysics\
EOSs share the same interface and can be compiled into \maestro\ directly.  
Here are the more popular EOSs:
\begin{itemize}
\item {\tt helmholtz} represents a general stellar equation 
      of state, consisting of nuclei (as an ideal gas), radiation,
      and electrons (with arbitrary degeneracy and degree of relativity).
      This equation of state is that described in \cite{timmes_eos}.

### 2016-07-17 Docs/getting_started/getting_started.tex
helmeos -> helmholtz

  Note, at the end of the build process, a link will be made in the
  current directory to the data table needed for the equation of state
  ({\tt Microphysics/EOS/helmeos/helm\_table.dat}).

>>>>

  Note, at the end of the build process, a link will be made in the
  current directory to the data table needed for the equation of state
  ({\tt Microphysics/EOS/helmholtz/helm\_table.dat}).
